Supplemental material

### 2024-08-22 paper/article_jos.qmd
final version

- The parameter $\delta$ can be estimated by moving average from @eq-mmsym. 
For example, for the LC method we can use the moving average $\boldsymbol \theta_2=\boldsymbol K\boldsymbol X(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{2}$ to obtain a local estimate of the slope and for the QL method we can use $\boldsymbol \theta_3=\boldsymbol K\boldsymbol X(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{3}$ to obtain a local estimate of the concavity. 
The DAF method then simply allows us to calculate the associated asymmetric moving averages.
To avoid unrealistic estimates of $|\delta/\sigma|=2/(|R|\sqrt{\pi})$ in real-time, with $R$ the I-C ratio defined in @sec-lppasymf, the value of $|R|$ is truncated to a maximum of 12 (the higher value used in X-11 being 4.5).
For the construction of moving averages, the trend can be modelled as being locally of degree 2 or 3 (this has no impact on the final estimate of concavity).
In this paper, we have chosen to model a trend of degree 2: this slightly reduces the phase shift (see supplemental material) but slightly increases the revisions linked to the first estimate of the trend-cycle. 
@Fig-mmpenteconcac shows the moving averages used.

@@

There is no function in `rjd3filters` to directly compute those moving averages but they can be easily computed using matrix computation formula and applied to the series using `rjd3filters`.

>>>>

- The parameter $\delta$ can be estimated by moving average from @eq-mmsym. 
For example, for the LC method we can use the moving average $\boldsymbol \theta_2=\boldsymbol K\boldsymbol X(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{2}$ to obtain a local estimate of the slope and for the QL method we can use $\boldsymbol \theta_3=\boldsymbol K\boldsymbol X(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{3}$ to obtain a local estimate of the concavity. 
The DAF method then simply allows us to calculate the associated asymmetric moving averages.\
To avoid unrealistic estimates of $|\delta/\sigma|=2/(|R|\sqrt{\pi})$ in real-time, where $R$ is the I-C ratio defined in @sec-lppasymf, the value of $|R|$ is truncated to a maximum of 12 (the higher value used in X-11 being 4.5), which slighly reduces revisions and phase shift.\
For the construction of moving averages, the trend can be modelled as being locally of degree 2 or 3 (this has no impact on the final estimate of concavity).
In this paper, we have chosen to model a trend of degree 2: this slightly reduces the phase shift (see supplemental material) but slightly increases the revisions linked to the first estimate of the trend-cycle. 
@Fig-mmpenteconcac shows the moving averages used.

@@

There is no function in `rjd3filters` to directly compute those moving averages but they can be easily computed using matrix computation formula and applied to the series using `rjd3filters`.
See for example the file `Simplified_example.R` available at <https://github.com/AQLT/joffstats2024>.

### 2024-08-22 paper/article_jos.tex
final version

This paper examines and compares real-time estimates of the trend-cycle
component using moving averages constructed with local polynomial
regression. It enables to reproduce Henderson's symmetric and Musgrave's
asymmetric filters used in the X-13ARIMA-SEATS seasonal adjustment
algorithm. This paper proposes two extensions of local polynomial
filters for real-time trend-cycle estimates: first including a
timeliness criterion to minimise the phase shift; second with procedure
for parametrising asymmetric filters locally while they are generally
parametrised globally, which can be suboptimal around turning points. An
empirical comparison, based on simulated and real data, shows that
modelling polynomial trends that are too complex introduces more
revisions without reducing the phase shift, and that local
parametrisation reduces the delay in detecting turning points and
reduces revisions. The results are reproducible and all the methods can
be easily applied using the R package \texttt{rjd3filters}.

@@

Using local polynomial regression, \textcite{proietti2008} developed a
general class of symmetric and asymmetric moving averages. In
particular, this class encompass Henderson's symmetric filter and
Musgrave's asymmetric filters. The aim of this study is to propose two
extensions to the \textcite{proietti2008} class of filters in order to
take account of two drawbacks of those methods. Firstly adding, in the
optimisation process, a timeliness criterion to directly control the
phase shift (i.e., the delay in detecting turning points). Secondly
calibrating asymmetric filters locally, while they are generally
calibrated globally using thus assumptions that may be wrong locally.
Those extensions are implemented in the statistical software R
\autocite{logicielr} throw the \texttt{rjd3filters} package
\autocite{rjd3filters} and can therefore be easily used. All the code
associated to this paper is available at \url{https://github.com/XXXX}
(anonymized linked before the manuscript is accepted).

@@

Numerous papers describe the definition and the properties of moving
averages and linear filters, see for example \textcite{ch12HBSA}. In
this section we summarize some of the main results to understand the
next sections.

Let \(p\) and \(f\) two integers, a moving average
\(M_{\boldsymbol\theta}\) is defined by a set of coefficients
\(\boldsymbol\theta=\transp{\begin{pmatrix}\theta_{-p}&\cdots&\theta_{f}\end{pmatrix}}\)
such as for all time series \(y_t\): \[
M_{\boldsymbol\theta}(y_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}.
\]

@@

To sum up, applying a moving average to a harmonic times series
(\(y_t=\e^{-i\omega t}\)) affects it in in two different ways:

@@

@@

\emph{Lecture: on monthly times series, 12-month cycles (associated to
the frequency \(2\pi/12=\pi/6\)) are amplified by 10\%
(\(G_{\boldsymbol\theta}(\pi/6)\simeq1.1\)) and associated turning
points are detected with a delay of 1 months
(\(\varphi_{\boldsymbol\theta}(\pi/6)/(\pi/6)\simeq -1\)).}
\emph{8-month cycles (associated to the irregular) are only reduced by
6\% (\(G_{\boldsymbol\theta}(\pi/4)\simeq0.94\)).}\\
\emph{Note: the Musgrave filter depends on a ratio denoted \(I/C\) (see
section~\ref{sec-nonparamreg}).} \emph{In X-11, for monthly series, when
the bandwidth is 6 (i.e.: a symmetric Henderson filter of order 13 is
used, what is used in most cases), the ratio is fixed to 3.5 and this
value is used in this figure.}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Use asymmetric moving averages to take account of the lack of
  available data;
\item
  Apply symmetric filters to an extended forecast series (which is
  equivalent to using asymmetric moving averages, since forecasts are
  linear combinations of the past). This method seems to date back to
  \textcite{deforest1877adjustment}, which also suggests modelling a
  polynomial trend of degree three or less at the end of the period. A
  similar approach is used in the X-13ARIMA-SEATS seasonal adjustment
  method: the series is extended by one year (by default) with an ARIMA
  model to minimise the revisions associated to asymmetric filters.
  Since the final filter used for the seasonal adjustment extraction is
  much longer than one year (in most of the cases, for monthly series,
  the bandwidth is 78), the input series is just partially extended (and
  asymmetric filters are still used) to prevent from instability over
  long periods (e.g., outliers or model shifts).
\end{enumerate}

@@

\begin{itemize}
\item
  If the ratio is large (\(3.5< R\)) then a 23-term filter is used (to
  remove more noise).
\item
  If the ratio is small (\(R<1\)) a 9-term filter is used.
\item
  Otherwise (most of the cases) a 13-term filter is used.
\end{itemize}

@@

\begin{itemize}
\item
  The variance \(\sigma^2\) can be estimated using the observed data set
  and the symmetric filter \((\theta_{-h},\dots,\theta_h)\). Indeed, as
  for example shown by \textcite{Loader1999}, the variance \(\sigma^2\)
  can be estimating using the normalized residual sum of squares: \[
  \hat\sigma^2=\frac{1}{(n-2h)-2\nu_1+\nu_2}\sum_{t=h+1}^{n-h}(y_t-\widehat{TC}_t)^2.
  \] Since the symmetric filter is used, only \(n-2h\) observations can
  be used to estimate \(\sigma^2\). \(\nu_1\) and \(\nu_2\) are two
  definitions of degrees of freedom of a local fit (generalization of
  the number of parameters of a parametric model). In the case of local
  polynomial smoothing, they can be linked to the coefficient of the
  associated filter: \(\nu_1 = (n-2h)\theta_0\) (number of observations
  multiplied by the central coefficient of the moving average) and
  \(\nu_2 = (n-2h)\sum_{i=-h}^{h} \theta_i^2\) (number of observations
  multiplied by the sum of squares of coefficients of the moving
  average). Thus, the variance can be estimated by: \[
  \hat\sigma^2=\frac{1}{n-2h}\sum_{t=h+1}^{n-h}\frac{(y_t-\widehat{TC}_t)^2}{1-2\theta_0^2+\sum_{i=-h}^{h} \theta_i^2}.
  \] This is implemented in the function
  \texttt{rjd3filters::var\_estimator()}. This estimator assumes that
  \(\widehat{TC}_t\) is unbiased, so variance estimates intervals are
  usually computed at small bandwidths (\(h\)). In this paper we study
  monthly series with small bandwidth (\(h=6\)), and the variance is
  estimated using local polynomial of degree 3 (Henderson filter), the
  biased of \(\widehat{TC}_t\) is thus already small and using smaller
  bandwidths have almost no impact on the estimates (see supplemental
  materials).
\item
  The parameter \(\delta\) can be estimated by moving average from
  equation~\ref{eq-mmsym}. For example, for the LC method we can use the
  moving average
  \(\boldsymbol \theta_2=\boldsymbol K\boldsymbol X(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{2}\)
  to obtain a local estimate of the slope and for the QL method we can
  use
  \(\boldsymbol \theta_3=\boldsymbol K\boldsymbol X(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{3}\)
  to obtain a local estimate of the concavity. The DAF method then
  simply allows us to calculate the associated asymmetric moving
  averages.\\
  For the construction of moving averages, the trend can be modelled as
  being locally of degree 2 or 3 (this has no impact on the final
  estimate of concavity). In this paper, we have chosen to model a trend
  of degree 2: this slightly reduces the phase shift (see supplemental
  material) but slightly increases the revisions linked to the first
  estimate of the trend-cycle. Figure~\ref{fig-mmpenteconcac} shows the
  moving averages used.
\end{itemize}

@@

There is no function in \texttt{rjd3filters} to directly compute those
moving averages but they can be easily computed using matrix computation
formula and applied to the series using \texttt{rjd3filters}.

@@

Excluding for the moment the local parametrisations of the polynomial
filters, the linear-constant polynomial filter (LC) seems to give the
best results in terms of delay in the detection of turning points
(figure~\ref{fig-graphstpsimul}). Performance is relatively close to
that obtained by extending the series using an ARIMA model. However,
when variability is low, the LC filter seems to give poorer results and
the quadratic-linear polynomial filter (QL) seems to give the best
results.

@@

\emph{Lecture: this plots represent box plots of the phase shift: the
box represents the interquartile range, the central horizontal line the
median the dot the outliers and the whisker the range of the data (if no
outlier).}\\
\emph{For simulated series with medium variability (when a symmetric
filter of length 13 is relevant), with the linear constant (LC) method,
50\% of the turning point are detected with a phase shift of at most 5
months whereas when the LC filter is parametrised locally, 50\% of the
turning point are detected with a phase shift of at most 4 months.}
\emph{For the direct asymmetric filter (DAF), 25\% of the turning are
detected with a phase shift of at least 7 months (compares to 5 for the
LC method).}

@@

In terms of revisions, the variability of the series has little effect
on the respective performances of the different methods, but it does
affect the orders of magnitude, which is why the results are presented
only for series with medium variability (table~\ref{tbl-simulrev}). In
general, LC filters always minimise revisions (with relatively small
effect from the local parametrisation of the filters) and revisions are
greater with cubic-quadratic (CQ) and direct (DAF) polynomial filters.

@@

\emph{Lecture: the estimates for \(q=0\) correspond to the first
estimates of the trend-cycle (real-time estimates when 0 point in the
future is known), \(q=1\) correspond to the second estimates of the
trend-cycle (when 1 point in the future is known).} \emph{Since the
final estimates are obtain using a symmetric filter of bandwidth 6,
\(q=6\) corresponds to the final estimates of the trend-cycle (when 6
points in the future are known).} \emph{\(MAE_{fe}(0)\) compares the
revision between the first estimate (\(q=0\)) and the last estimate
(\(q=6\)) and \(MAE_{ce}(0)\) compares the revision between the first
estimate (\(q=0\)) and the second estimate (\(q=1\)).}

@@

\caption{\label{fig-ce16ovlp}Successive estimates of the trend-cycle in
US employment (in logarithms).}

@@

\emph{Lecture: the dotted vertical line corresponds to the date of the
turning point (February 2001).} \emph{The curve ``Feb 2001'' corresponds
to the estimates of the trend-cycle using the data observed until
February 2001.} \emph{Since a 13-term Henderson filter is used for the
final estimates, for the curve ``Feb 2001'' estimates from September
2001 to February 2001 are intermediate estimates.}

@@

\caption{\label{fig-ce16ov-previmp-lp}Implicit forecasts linked to
successive estimates of the trend-cycle in US employment (in logarithms)
using local polynomial methods.}

@@

\emph{Lecture: the dotted vertical line corresponds to the date of the
turning point (February 2001).} \emph{The curve ``Mar 2001'' corresponds
to the implicit forecasts associated to the asymmetric filters used for
the trend-cycle estimations using the data observed until March 2001.}

@@

Since X-13ARIMA-SEATS can only be applied for series with frequency
lower than monthly, for higher frequencies (weekly, daily, etc.), there
is no reference on the length of the filters to uses. The length of the
filters can be determined using local polynomial methods, for example
minimising a cross-validation statistics (using the function
\texttt{rjd3filters::cross\_validation()}) or with more complex methods
as describe by \textcite{Loader1999}, but it will surely be necessary to
use higher bandwidth than for monthly series. The larger the window, the
greater the bias in assuming that the trend is locally of degree 1: the
LC method will then be certainly less appropriate than other methods
(QL, CQ or DAF). Moreover, since the bias is higher, the local
parametrisation of the filters will surely have more impact.

@@

Figure~\ref{fig-ce16ovcovid} and figure~\ref{fig-ce16ov-previmp-covid}
show the successive estimates of the trend-cycle and the associated
implicit forecast for the US employment during the COVID-19. First, we
observe that while the real turning point is in April 2020, the 13-term
Henderson filter produces final estimates of the trend-cycles, biased by
the presence of a huge outlier, which lead to a turning point detected
in June 2020. Second, as in 2001, the CQ and DAF methods lead to lots of
variability in the intermediate estimates. For the QL method, the local
parametrisation seems to slightly reduce the revisions. For the LC
method, local parametrisation has few impact on the estimates of the
trend-cycle but the associated implicit forecasts are not plausible: the
final estimate of the slope is biased by the outlier. Third, the ARIMA
model can lead to unrealistic forecasts.

@@

\begin{itemize}
\item
  Adjustment of outliers prior to filtering, for example with a RegARIMA
  model or other correction modules like the one used in X-11.
\item
  Increase the bandwidth of the filter used to extract the trend-cycle
  (it will smooth the trend-cycle by giving less weights to the atypical
  points).
\item
  Since all the filter studied in this paper are equivalent to a local
  polynomial model, an external regressor can be added to the linear
  model to handle the outlier (the matrix \(\boldsymbol X\) would then
  be modified). In the case of an additive outlier, this is equivalent
  to set to 0 the coefficient of the moving average associated to the
  date of the outlier (using \(y_{t-h}\) to \(y_{t+h}\) for the
  trend-cycle estimates, if the outlier is at the date \(t\) the central
  coefficient is set to 0) and renormalise the sum of the coefficients
  to 1.
\item
  Use of robust methods to estimate the trend-cycle, such as robust
  local regressions or moving medians.
\end{itemize}

>>>>

This paper examines and compares real-time estimates of the trend-cycle
component using moving averages constructed with local polynomial
regression. It enables the reproduction of Henderson's symmetric and
Musgrave's asymmetric filters used in the X-13ARIMA-SEATS seasonal
adjustment algorithm. This paper proposes two extensions of local
polynomial filters for real-time trend-cycle estimates: first including
a timeliness criterion to minimise the phase shift; second with
procedure for parametrising asymmetric filters locally while they are
generally parametrised globally, which can be suboptimal around turning
points. An empirical comparison, based on simulated and real data, shows
that modelling polynomial trends that are too complex introduces more
revisions without reducing the phase shift, and that local
parametrisation reduces the delay in detecting turning points and
reduces revisions. The results are reproducible and all the methods can
be easily applied using the R package \texttt{rjd3filters}.

@@

In the last decades, numerous authors proposed methods for the
construction of alternative moving averages to derive trend-cycle
estimates. In particular, \textcite{trilemmaWMR2019} put forth a
model-based approach based on the mean squared error decomposition,
while \textcite{proietti2008}, \textcite{dagumbianconcini2008} and
\textcite{ch15HBSA} proposed non-parametric methods based, respectively,
on local polynomial regression, Reproducing Kernel Hilbert Space (RKHS)
theory and minimising of a weighted sum of moving average quality
criteria. All of the aforementioned approaches encompass both
Henderson's symmetric filter and Musgrave's asymmetric filters. More
recently, \textcite{inseeDTM202401} conducted a comparative analysis of
these methods by describing a general unifying framework to derive
moving averages; \textcite{dagumBianconcini2023} provided statistical
tests to assess the main properties of the filters defined in terms of
revisions and the detection of turning points.

The aim of this study is to propose two extensions to the
\textcite{proietti2008} class of filters in order to take account of two
drawbacks of those methods: firstly adding, in the optimisation process,
a timeliness criterion to directly control the phase shift (i.e., the
delay in detecting turning points); secondly calibrating asymmetric
filters locally, while they are generally calibrated globally using
assumptions that may be wrong locally. Those extensions are implemented
in the statistical software R \autocite{logicielr} through the
\texttt{rjd3filters} package \autocite{rjd3filters} and can therefore be
easily used. All the code associated to this paper is available at
\url{https://github.com/AQLT/joffstats2024}.

@@

Numerous papers describe the definition and the properties of moving
averages and linear filters; see for example \textcite{ch12HBSA}. In
this section we summarize some of the main results to understand the
next sections.

Let \(p\) and \(f\) two integers, a moving average
\(M_{\boldsymbol\theta}\) is defined by a set of coefficients
\(\boldsymbol\theta=\transp{\begin{pmatrix}\theta_{-p}&\cdots&\theta_{f}\end{pmatrix}}\)
such that for all time series \(y_t\): \[
M_{\boldsymbol\theta}(y_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}.
\]

@@

To sum up, applying a moving average to a harmonic times series
(\(y_t=\e^{-i\omega t}\)) affects it in two different ways:

@@

Observed in figure~\ref{fig-graphsmusgrave} that for monthly times
series, 12-month cycles (associated to the frequency \(2\pi/12=\pi/6\))
are amplified by 10\% (\(G_{\boldsymbol\theta}(\pi/6)\simeq1.1\)) and
associated turning points are detected with a delay of 1 months
(\(\varphi_{\boldsymbol\theta}(\pi/6)/(\pi/6)\simeq -1\)). 8-month
cycles (associated to the irregular) are only reduced by 6\%
(\(G_{\boldsymbol\theta}(\pi/4)\simeq0.94\)). Note that the Musgrave
filter depends on a ratio denoted \(I/C\) (see
section~\ref{sec-nonparamreg}). In X-11, for monthly series, when the
bandwidth is 6 (i.e.: a symmetric Henderson filter of order 13 is used,
what is used in most cases), the ratio is fixed to 3.5 and this value is
used in this figure.

@@

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Use asymmetric moving averages to take account of the lack of
  available data;
\item
  Apply symmetric filters to an extended forecast series (which is
  equivalent to using asymmetric moving averages, since forecasts are
  linear combinations of the past). This method seems to date back to
  \textcite{deforest1877adjustment}, which also suggests modelling a
  polynomial trend of degree three or less at the end of the period. A
  similar approach is used in the X-13ARIMA-SEATS seasonal adjustment
  method: the series is extended by one year (by default) with an ARIMA
  model to minimise the revisions associated to asymmetric filters.
  Since the final filter used for the seasonal adjustment extraction is
  much longer than one year (in most of the cases, for monthly series,
  the bandwidth is 78), the input series is just partially extended (and
  asymmetric filters are still used) to prevent instability over long
  periods (e.g., outliers or model shifts).
\end{enumerate}

@@

\begin{itemize}
\item
  If the ratio is large (\(3.5< R\)) then a 23-term filter is used (to
  remove more noise) and the ratio \(R=4.5\) is used in X-11 to define
  the Musgrave filter.
\item
  If the ratio is small (\(R<1\)) a 9-term filter is used and the ratio
  \(R=1\) is used in X-11 to define the Musgrave filter.
\item
  Otherwise (most of the cases) a 13-term filter is used and the ratio
  \(R=3.5\) is used in X-11 to define the Musgrave filter.
\end{itemize}

@@

\begin{itemize}
\item
  The variance \(\sigma^2\) can be estimated using the observed data set
  and the symmetric filter \((\theta_{-h},\dots,\theta_h)\). Indeed, as
  for example shown by \textcite{Loader1999}, the variance \(\sigma^2\)
  can be estimating using the normalized residual sum of squares: \[
  \hat\sigma^2=\frac{1}{(n-2h)-2\nu_1+\nu_2}\sum_{t=h+1}^{n-h}(y_t-\widehat{TC}_t)^2.
  \] Since the symmetric filter is used, only \(n-2h\) observations can
  be used to estimate \(\sigma^2\). \(\nu_1\) and \(\nu_2\) are two
  definitions of degrees of freedom of a local fit (generalization of
  the number of parameters of a parametric model). In the case of local
  polynomial smoothing, they can be linked to the coefficient of the
  associated filter: \(\nu_1 = (n-2h)\theta_0\) (number of observations
  multiplied by the central coefficient of the moving average) and
  \(\nu_2 = (n-2h)\sum_{i=-h}^{h} \theta_i^2\) (number of observations
  multiplied by the sum of squares of coefficients of the moving
  average). Thus, the variance can be estimated by: \[
  \hat\sigma^2=\frac{1}{n-2h}\sum_{t=h+1}^{n-h}\frac{(y_t-\widehat{TC}_t)^2}{1-2\theta_0^2+\sum_{i=-h}^{h} \theta_i^2}.
  \] This is implemented in the function
  \texttt{rjd3filters::var\_estimator()}. This estimator assumes that
  \(\widehat{TC}_t\) is unbiased, so variance estimates intervals are
  usually computed at small bandwidths (\(h\)). In this paper we study
  monthly series with small bandwidth (\(h=6\)), and the variance is
  estimated using local polynomial of degree 3 (Henderson filter), the
  biased of \(\widehat{TC}_t\) is thus already small and using smaller
  bandwidths have almost no impact on the estimates (see supplemental
  materials).
\item
  The parameter \(\delta\) can be estimated by moving average from
  equation~\ref{eq-mmsym}. For example, for the LC method we can use the
  moving average
  \(\boldsymbol \theta_2=\boldsymbol K\boldsymbol X(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{2}\)
  to obtain a local estimate of the slope and for the QL method we can
  use
  \(\boldsymbol \theta_3=\boldsymbol K\boldsymbol X(\transp{\boldsymbol X}\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{3}\)
  to obtain a local estimate of the concavity. The DAF method then
  simply allows us to calculate the associated asymmetric moving
  averages.\\
  To avoid unrealistic estimates of
  \(|\delta/\sigma|=2/(|R|\sqrt{\pi})\) in real-time, where \(R\) is the
  I-C ratio defined in section~\ref{sec-lppasymf}, the value of \(|R|\)
  is truncated to a maximum of 12 (the higher value used in X-11 being
  4.5), which slighly reduces revisions and phase shift.\\
  For the construction of moving averages, the trend can be modelled as
  being locally of degree 2 or 3 (this has no impact on the final
  estimate of concavity). In this paper, we have chosen to model a trend
  of degree 2: this slightly reduces the phase shift (see supplemental
  material) but slightly increases the revisions linked to the first
  estimate of the trend-cycle. Figure~\ref{fig-mmpenteconcac} shows the
  moving averages used.
\end{itemize}

@@

There is no function in \texttt{rjd3filters} to directly compute those
moving averages but they can be easily computed using matrix computation
formula and applied to the series using \texttt{rjd3filters}. See for
example the file \texttt{Simplified\_example.R} available at
\url{https://github.com/AQLT/joffstats2024}.

@@

Figure~\ref{fig-graphstpsimul} represents box plots of the phase shift:
the box represents the interquartile range, the central horizontal line
the median the dot the outliers and the whisker the range of the data
(if no outlier). For simulated series with medium variability (when a
symmetric filter of length 13 is relevant), with the linear constant
(LC) method, 50\% of the turning point are detected with a phase shift
of at most 5 months whereas when the LC filter is parametrised locally,
50\% of the turning point are detected with a phase shift of at most 4
months. For the direct asymmetric filter (DAF), 25\% of the turning are
detected with a phase shift of at least 7 months (compares to 5 for the
LC method).

Excluding for the moment the local parametrisations of the polynomial
filters, the linear-constant polynomial filter (LC) seems to give the
best results in terms of delay in the detection of turning points.
Performance is relatively close to that obtained by extending the series
using an ARIMA model. However, when variability is low, the LC filter
seems to give poorer results and the quadratic-linear polynomial filter
(QL) seems to give the best results.

@@

@@

Observe table~\ref{tbl-simulrev} the average of the relative deviations
with medium variability. The estimates for \(q=0\) correspond to the
first estimates of the trend-cycle (real-time estimates when 0 point in
the future is known), \(q=1\) correspond to the second estimates of the
trend-cycle (when 1 point in the future is known). Since the final
estimates are obtain using a symmetric filter of bandwidth 6, \(q=6\)
corresponds to the final estimates of the trend-cycle (when 6 points in
the future are known). \(MAE_{fe}(0)\) compares the revision between the
first estimate (\(q=0\)) and the last estimate (\(q=6\)) and
\(MAE_{ce}(0)\) compares the revision between the first estimate
(\(q=0\)) and the second estimate (\(q=1\)).

In terms of revisions, the variability of the series has little effect
on the respective performances of the different methods, but it does
affect the orders of magnitude, which is why the results are presented
only for series with medium variability. In general, LC filters always
minimise revisions (with relatively small effect from the local
parametrisation of the filters) and revisions are greater with
cubic-quadratic (CQ) and direct (DAF) polynomial filters.

@@

@@

\caption{\label{fig-ce16ovlp}Successive estimates of the trend-cycle in
US employment (in logarithms). The dotted vertical line corresponds to
the date of the turning point (February 2001). The curve ``Feb 2001''
corresponds to the estimates of the trend-cycle using the data observed
until February 2001. Since a 13-term Henderson filter is used for the
final estimates, for the curve ``Feb 2001'' estimates from September
2001 to February 2001 are intermediate estimates.}

@@

@@

\caption{\label{fig-ce16ov-previmp-lp}Implicit forecasts linked to
successive estimates of the trend-cycle in US employment (in logarithms)
using local polynomial methods. The dotted vertical line corresponds to
the date of the turning point (February 2001). The curve ``Mar 2001''
corresponds to the implicit forecasts associated to the asymmetric
filters used for the trend-cycle estimations using the data observed
until March 2001.}

@@

@@

Since X-13ARIMA-SEATS can only be applied for series with frequency
lower than monthly, for higher frequencies (weekly, daily, etc.), there
is no reference on the length of the filters to uses. The length of the
filters can be determined using local polynomial methods, for example
minimising a statistic such as cross-validation
(\texttt{rjd3filters::cv()}), CP (\texttt{rjd3filters::cp()}) or Rice's
T (\texttt{rjd3filters::rt()}), or with more complex methods as describe
by \textcite{Loader1999}, but it will surely be necessary to use higher
bandwidth than for monthly series. The larger the window, the greater
the bias in assuming that the trend is locally of degree 1: the LC
method will then be certainly less appropriate than other methods (QL,
CQ or DAF). Moreover, since the bias is higher, the local
parametrisation of the filters will surely have more impact.

@@

Figure~\ref{fig-ce16ovcovid} and figure~\ref{fig-ce16ov-previmp-covid}
show the successive estimates of the trend-cycle and the associated
implicit forecast for the US employment during the COVID-19. First, we
observe that while the real turning point is in April 2020, the 13-term
Henderson filter produces final estimates of the trend-cycles, biased by
the presence of a huge outlier, which lead to a turning point detected
in June 2020. Second, as in 2001, the CQ and DAF methods lead to lots of
variability in the intermediate estimates. For the QL method, the local
parametrisation seems to slightly reduce the revisions. For the LC
method, local parametrisation has little impact on the estimates of the
trend-cycle but the associated implicit forecasts are not plausible: the
final estimate of the slope is biased by the outlier. Third, the ARIMA
model can lead to unrealistic forecasts.

@@

\begin{itemize}
\item
  Adjustment of outliers prior to filtering, for example with a RegARIMA
  model or other correction modules like the one used in X-11.
\item
  Increase the bandwidth of the filter used to extract the trend-cycle
  (it will smooth the trend-cycle by giving less weights to the atypical
  points).
\item
  Since all the filters studied in this paper are equivalent to a local
  polynomial model, an external regressor can be added to the linear
  model to handle the outlier (the matrix \(\boldsymbol X\) would then
  be modified). In the case of an additive outlier, this is equivalent
  to setting to 0 the coefficient of the moving average associated to
  the date of the outlier (using \(y_{t-h}\) to \(y_{t+h}\) for the
  trend-cycle estimates, if the outlier is at the date \(t\) the central
  coefficient is set to 0) and renormalise the sum of the coefficients
  to 1.
\item
  Use of robust methods to estimate the trend-cycle, such as robust
  local regressions or moving medians.
\end{itemize}

### 2024-08-22 paper/supp_material.qmd
final version

---
title: "Supplemental material"
format:
  pdf:
    documentclass: article
    number-sections: true
    pdf-engine: pdflatex
    toc: false
    include-in-header: [preamble.tex]
    #include-before-body: template/preambule.tex
    geometry:
      - top=2cm
      - bottom=2cm
      - left = 2.5cm
      - right = 2.5cm
linestretch: 2
echo: false
tbl-cap-location: top
fig-cap-location: top
---

>>>>

---
title: "Supplemental material"
format:
  pdf:
    documentclass: article
    number-sections: true
    pdf-engine: pdflatex
    toc: false
    keep-tex: true
    include-in-header: [preamble.tex]
    #include-before-body: template/preambule.tex
    geometry:
      - top=2cm
      - bottom=2cm
      - left = 2.5cm
      - right = 2.5cm
linestretch: 2
echo: false
tbl-cap-location: top
fig-cap-location: top
---
